### 2011-04-04 msm2aa.tex
Nearly done 2Aa first draft.

		\subsubsection{Fubini's theorem}
		\begin{thm}
			Let $f:\mathbb{R}^2 \to \mathbb{R}$ be continuous on $D$, which is given as
			\[
				D = {(x,y): a \leq x \leq b, c(x) \leq y \leq d(x)},
			\]
			where $c(x)$ and $d(x)$ are smooth. If $\iint\limits_D f(x,y) dxdy$ exists, then
			\[
				\iint\limits_D f(x,y) dxdy = \int\limits_a^b \left( \int\limits_{c(x)}^{d(x)} f (x,y) dy \right) dx = \int\limits_a^b dx \int\limits_{c(x)}^{d(x)} f (x,y) dy
			\]
		\end{thm}

@@

>>>>

		\subsubsection{Fubini's theorem}
		\begin{thm}
			Let $f:\mathbb{R}^2 \to \mathbb{R}$ be continuous on $D$, which is given as
			\[
				D = \{(x,y): a \leq x \leq b, c(x) \leq y \leq d(x)\},
			\]
			where $c(x)$ and $d(x)$ are smooth. If $\iint\limits_D f(x,y) dxdy$ exists, then
			\[
				\iint\limits_D f(x,y) dxdy = \int\limits_a^b \left( \int\limits_{c(x)}^{d(x)} f (x,y) dy \right) dx = \int\limits_a^b dx \int\limits_{c(x)}^{d(x)} f (x,y) dy
			\]
		\end{thm}

		\begin{thm}
			Let $f:\mathbb{R}^2 \to \mathbb{R}$ be continuous on $D$, which is given as
			\[
				D = \{(x,y): c \leq y \leq d, a(y) \leq y \leq b(y)\},
			\]
			where $a(y)$ and $b(y)$ are smooth. If $\iint\limits_D f(x,y) dxdy$ exists, then
			\[
				\iint\limits_D f(x,y) dxdy = \int\limits_c^d dy \int\limits_{a(y)}^{b(y)} f (x,y) dx
			\]
		\end{thm}

		\subsubsection{Fubini's theorem for triple integrals}
		\[
			\iiint\limits_S f(x,y,z) dxdydz \equiv \int\limits_{x=a}^{x=b} dx \int\limits_{y=l(x)}^{y=r(x)} dy \int\limits_{z=g(x,y)}^{z=h(x,y)} f(x,y,z) dz
											\equiv \int\limits_{a}^{b} dx \int\limits_{l(x)}^{r(x)} dy \int\limits_{g(x,y)}^{h(x,y)} f(x,y,z) dz
		\]
		The order of integration does not matter. Choose the easiest order.

@@

	\subsection{Double integrals in polar coordinates}
		\subsubsection{Polar coordinates}
		The relation between polar coordinates and Cartesian coordinates are:
		\[
			x = r \cos{\theta}, y = r \sin{\theta}
		\]
		or
		\[
			r = sqrt{x^2 + y^2}, \tan{\theta} = \frac{y}{x}
		\]
		where $r \geq 0$, $0 \leq \theta \leq 2 \pi$ or $-\pi \le \theta \leq \pi$.

		\subsubsection{Double integrals in polar coordinates}
		For double integrals in polar coordinates
		\[
			dA = dxdy = rdrd \theta
		\]
		\[
			\iint\limits_D f(x,y) dxdy = \iint\limits_{D'} f(r,\theta) rdrd \theta
		\]
		where $D'$ is the region of the $(r,\theta)$-plane corresponding to the region of $D$ of the $(x,y)$-plane.

		\subsubsection{General case}
		\begin{defn}
			The Jacobian of the functions $x(u,v)$ and $y(u,v)$ with respect to the variables $u$ and $v$ is the determinant. Hence,
			\[
				\frac{\partial (u,v)}{\partial (x,y)} = 
				\begin{vmatrix}
					x_u & x_v  \\
					y_u & y_v 
				\end{vmatrix} 
			\]
		\end{defn}
		For double integrals we have
		\[
			dA = dxdy = \left| \frac{\partial (u,v)}{\partial (x,y)} \right| dudv
		\]
		\[
			\iint\limits_D f(x,y) dxdy = \iint\limits_{D'} f(x,y) | \frac{\partial (x,y)}{\partial (u,v)} | dudv
		\]
		where $D'$ is the region of the $(u,v)$-plane corresponding to the region of $D$ of the $(x,y)$-plane.

	\subsection{Change of variables in triple integrals}
		\subsubsection{Cylindrical coordinates}
		Consider the point $P$ with Cartesian coordinates $(x,y,z)$, $Q$ is the projection of $P$ on the $Oxy$ plane. Denote its cylindrical coordinates as $(\rho, \theta, z)$, then:
		\[
			\left\{ 
				\begin{matrix}
					x = r \cos{\theta} \\
					y = r \sin{\theta} \\ 
					z = z
				\end{matrix} 
			\right.
				\iff
			\left\{ 
				\begin{matrix}
					r = \sqrt{x^2 + y^2}  \\
					\tan{\theta} = \frac{y}{x} \\
					z = z
				\end{matrix} 
			\right.
		\]
		where $r \ge 0$, $0 \le \theta < 2 \pi$, $-\infty < z < \infty$.

		\subsubsection{Jacobian for triple integrals}
		\begin{defn}
			The Jacobian of the functions $x(u,v,w)$, $y(u,v,w)$, and $z(u,v,w)$ with respect to the variables $u$, $v$, and $w$ is the determinant. Hence,
			\[
				\frac{\partial (u,v,w)}{\partial (x,y,z)} = 
				\begin{vmatrix}
					x_u & x_v & x_w \\
					y_u & y_v & y_w \\
					z_u & z_v & z_w					
				\end{vmatrix} 
			\]
		\end{defn}

		For triple integrals we have that 
		\[
			dV = dxdydz = \left| \frac{\partial (x,y,z)}{\partial (u,v,w)} \right| dudvdw
		\]
		Hence,
		\[
			\iiint\limits_S f(x,y,z) dxdydz = \iiint\limits_{S'} f(x(u,v,w), y(u,v,w), z(u,v,w)) \left| \frac{\partial (x,y,z)}{\partial (u,v,w)} \right| dudvdw
		\]
		where $S'$ is the region of the $(u,v,w)$-plane corresponding to the region of $S$ of the $(x,y,z)$-plane.

		\subsubsection{Triple integrals in cylindrical coordinates}
		For the cylindrical coordinates we have that $x=r \cos{\theta}$, $y=r \sin{\theta}$, and $z=z$.
		Hence,
		\[
			\frac{\partial (x,y,z)}{\partial (r,\theta,z)} = 
				\begin{vmatrix}
					x_r & x_\theta & x_z \\
					y_r & y_\theta & y_z \\
					z_r & z_\theta & z_z					
				\end{vmatrix}
				=
				\begin{vmatrix}
					x_r & x_\theta & 0 \\
					y_r & y_\theta & 0 \\
					0 & 0 & 1					
				\end{vmatrix} = r
		\]
		Finally giving that
		\[	
			dV = dxdydz = rdrd\theta dz
		\]
		Hence,
		\[
			\iiint\limits_S f(x,y,z) dxdydz = \iiint\limits_{S'} f(r, \theta, z) r drd\theta dz
		\]

		\subsubsection{Spherical coordinates}
		Spherical coordinates $(\rho, \theta, \phi)$
		\[
			x = \rho \sin{\phi} \cos{\theta}, \quad y = \rho \sin{\phi} \sin{\theta}, \quad z = \rho \cos{\phi}
		\]
		where $\rho \ge 0$, $0 \le \theta \le 2 \Pi$, $0 \le \phi \le \Pi$.

		Relation between Cartesian and spherical coordinates
		\begin{align*}
			\rho &= \sqrt{x^2 + y^2 + z^2} \\
			\theta &= \arctan{ \left( \frac{y}{z} \right)} \\
			\phi &= \arccos{ \left(\frac{z}{\rho} \right)}
		\end{align*}

		Relation between cylindrical and spherical coordinates
		\begin{align*}
			r &= \rho \sin{\phi} \\ 
			\theta &= \theta \\
			z &= \rho \cos{\phi}
		\end{align*}

		\subsubsection{Jacobian of spherical coordinates}
		Using
		\[
			x = \rho \sin{\phi} \cos{\theta}, \quad y = \rho \sin{\phi} \sin{\theta}, \quad z = \rho \cos{\phi}
		\]
		we have that
		\[
			\frac{\partial (x,y,z)}{\partial (\rho,\phi,\theta)} = \rho^2 \sin{\theta}
		\]

		\subsubsection{Triple integrals in spherical coordinates}
		From the above result, we have that
		\[
			dV = \rho^2 \sin{\theta} d\rho d\phi d\theta
		\]
		Hence
		\[
			\iiint\limits_S f(x,y,z) dxdydz = \iiint\limits_{S'} f( \rho, \phi, \theta) \rho^2 \sin{\theta} d\rho d\phi d\theta
		\]

	\subsection{Line integrals}
		\subsubsection{Fields}
		\begin{defn}
			A scalar function depending on a position is called a scalar field. A vector function depending on a position is called a vector field.
		\end{defn}

		\subsubsection{Tangential vector}
		If $\mathbf{r} = (x(t), y(t), z(t)), \quad t \in [t_0, t_1]$ is a parameterisatino of the curve $C$ (preserving orientation) then
		\begin{itemize}
			\item The tangential vector of the curve is $\mathbf{T}(t) = \frac{d\mathbf{r}}{dt} = \left( \frac{dx}{dt}, \frac{dy}{dt}, \frac{dz}{dt} \right)$
			\item It's magnitude is $\left| \mathbf{T} \right| = \left| \frac{d\mathbf{r}}{dt} \right| = \sqrt{ \left( \frac{dx}{dt} \right)^2 + \left( \frac{dy}{dt} \right)^2 + \left( \frac{dz}{dt} \right)^2   }$
			\item The length $ds$ is $ds = \left| d\mathbf{r} \right| = \left| \frac{d\mathbf{r}}{dt} \right|dt = \left| \mathbf{T} \right| dt$
		\end{itemize}

		\subsubsection{Line integrals}

		\subsubsection{Line integrals of vector fields}
		\subsubsection{Other expressions of line integrals}
		\subsubsection{Work done by a force}
